Pool Model Paper

### 2023-10-27 pool_model.tex
add matrix forms to equations

Such model can be simplified by explointing that limitation of the resource pool also limits the total bacterial count of the system:
\begin{equation}
    R = 1 - \frac{L+G+D}{N_t}
\end{equation}
and, hence, the full system can be written as
\begin{equation}
    \begin{cases}
        \dot{L} = -(\mu + \lambda) L\\
        \dot{G} = \lambda L + \alpha G\left(1-\frac{L+G+D}{N_t}\right)-\mu' G\\
        \dot{D} = \mu  L + \mu' G- \beta D 
        \label{eq:3pool_resource} 
    \end{cases}.
\end{equation}

@@

\begin{equation}
    \begin{cases}
        \dot{L}_A = - \lambda_A R L_A\\
        \dot{L}_B = - \lambda_B R L_B \\
        \dot{G}_A = \lambda_A R L_A +\alpha_A R G_A\\
        \dot{G}_B = \lambda_B R L_B +\alpha_B R G_B\\
        \dot{R} =-\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{N_t} R G_B
    \end{cases}
    \label{eq:model_2sp_resource_comp}
\end{equation}

We again rescaled the resource pool with $N_t$ and find
\begin{eqnarray}
\label{Resource}
R &=&1-\frac{L_A+G_A+L_B+G_B}{N_t}
\end{eqnarray}
Inserting Eq. \ref{Resource} into Eqs. \ref{eq:model_2sp_resource_comp} yields:
\begin{eqnarray*}
\dot{L}_A &=& - \lambda_A  L_A + \frac{\lambda_A}{N_t}\left(L_A+G_A+L_B+G_B\right )L_A\\
\dot{L}_B &=& - \lambda_B L_B + \frac{\lambda_B}{N_t}\left(L_A+G_A+L_B+G_B\right )L_B \\
\dot{G}_A &=&  \lambda_A  L_A - \frac{\lambda_A}{N_t}\left(L_A+G_A+L_B+G_B\right )L_A +\alpha_A G_A - \frac{\alpha_A}{N_t}\left(L_A+G_A+L_B+G_B\right )G_A\\
\dot{G}_B &=& \lambda_B L_B - \frac{\lambda_B}{N_t}\left(L_A+G_A+L_B+G_B\right )L_B  +\alpha_B G_B -\frac{\alpha_B}{N_t}\left(L_A+G_A+L_B+G_B\right )G_B
\end{eqnarray*}

>>>>

Such model can be simplified by explointing that limitation of the resource pool also limits the total bacterial count of the system:
\begin{equation}
    R = 1 - \frac{L+G+D}{N_t}
\end{equation}
and, hence, the full system can be written as 
\begin{equation}
    \begin{cases}
        \dot{L} = -(\mu + \lambda) L\\
        \dot{G} = \lambda L + \alpha G\left(1-\frac{L+G+D}{N_t}\right)-\mu' G\\
        \dot{D} = \mu  L + \mu' G- \beta D 
        \label{eq:3pool_resource} 
    \end{cases}.
\end{equation}
Rewriting the equations above, we get the following non-linear system:
\begin{equation}
    \dot \mbx = \begin{pmatrix}
        -(\mu + \lambda) & 0       & 0 \\
         \lambda         & \alpha  & 0 \\
         \mu & + \mu'& - \beta 
    \end{pmatrix} 
    \mbx + \frac{\alpha}{N_t} x^2 \sum_i^3 x^i \begin{pmatrix} 0 \\ 1 \\ 0  \end{pmatrix}.
\end{equation}
Here the first term is the linear part and the second term define the quadratic behaviour of the system.

@@

\begin{equation}
    \begin{cases}
        \dot{L}_A = - \lambda_A R L_A\\
        \dot{L}_B = - \lambda_B R L_B \\
        \dot{G}_A = \lambda_A R L_A +\alpha_A R G_A\\
        \dot{G}_B = \lambda_B R L_B +\alpha_B R G_B\\
        \dot{R} =-\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{N_t} R G_B
    \end{cases}
    \label{eq:model_2sp_resource_comp}
\end{equation}
This system of equations defines the microenvironment $\mbm$ and bacteria state matrix $\mbx$ as
\begin{equation}
    \mbm = R, \hspace{1cm}
    \mbx = \begin{pmatrix}
        L_A & L_B \\
        G_A & G_B 
    \end{pmatrix}.
\end{equation}
We again rescaled the resource pool with $N_t$ and find
\begin{eqnarray}
\label{Resource}
R &=&1-\frac{L_A+G_A+L_B+G_B}{N_t}
\end{eqnarray}
Inserting Eq. \ref{Resource} into Eqs. \ref{eq:model_2sp_resource_comp} yields:
\begin{eqnarray*}
\dot{L}_A &=& - \lambda_A  L_A + \frac{\lambda_A}{N_t}\left(L_A+G_A+L_B+G_B\right )L_A\\
\dot{L}_B &=& - \lambda_B L_B + \frac{\lambda_B}{N_t}\left(L_A+G_A+L_B+G_B\right )L_B \\
\dot{G}_A &=&  \lambda_A  L_A - \frac{\lambda_A}{N_t}\left(L_A+G_A+L_B+G_B\right )L_A +\alpha_A G_A - \frac{\alpha_A}{N_t}\left(L_A+G_A+L_B+G_B\right )G_A\\
\dot{G}_B &=& \lambda_B L_B - \frac{\lambda_B}{N_t}\left(L_A+G_A+L_B+G_B\right )L_B  +\alpha_B G_B -\frac{\alpha_B}{N_t}\left(L_A+G_A+L_B+G_B\right )G_B
\end{eqnarray*}
